Graphs for 1000  Generations

### 2021-07-11 graphs_newt_snakes/fig_1000.Rmd
still adding more to the r functions. getting closer to working

  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  mean = mean(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno), na.rm = TRUE)
  sd = sd(c(file$Newt_mean_Pheno, file$Snake_mean_Pheno), na.rm = TRUE)
  mean_mean_dif = mean(as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno),na.rm = TRUE)
  sd_mean_dif = sd(as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno),na.rm = TRUE)

  if (max(file$Newt_max_Pheno) > newt_max_pheno_1){
    newt_max_pheno_1 = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno_1){
    snake_max_pheno_1 = max(file$Snake_max_Pheno) }

  if (min(file$Newt_min_Pheno) < newt_min_pheno_1){
    newt_min_pheno_1 = min(file$Newt_min_Pheno) }

  if (min(file$Snake_min_Pheno) > snake_min_pheno_1){
    snake_min_pheno_1 = max(file$Snake_min_Pheno) }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_1){
    min_difference_1 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_1){
    max_difference_1 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }
  }

@@

@@

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred") + 
  ggtitle("Wrong1sim: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()
q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(Snake_mean_Pheno)*10)), color = "steelblue") + 
  ggtitle("Wrong1sim: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
 p <- p + geom_line(data=file, aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred")

 q <- q + geom_line(data=file, aes(y = (log(Snake_mean_Pheno)*10)), color="steelblue", linetype="twodash")
}

@@

```{r data 1 msprime photype graph, echo=FALSE}
newt_max_pheno_2 = 0
snake_max_pheno_2 = 0
newt_min_pheno_2 = 0
snake_min_pheno_2 = 0
true_max_2 = 0
true_min_2 = 0
min_difference_2 = 0
max_difference_2 = 0

  file <- read.table(current_file, header = TRUE)
  #print(max(file$Newt_max_Pheno))
  #print(max(file$Snake_max_Pheno))

  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA

  if (max(file$Newt_max_Pheno) > newt_max_pheno_2){
    newt_max_pheno_2 = max(file$Newt_max_Pheno) }

  if (max(file$Snake_max_Pheno) > snake_max_pheno_2){
    snake_max_pheno_2 = max(file$Snake_max_Pheno) }

  if (min(file$Newt_min_Pheno) < newt_min_pheno_2){
    newt_min_pheno_2 = max(file$Newt_min_Pheno) }

  if (max(file$Snake_min_Pheno) < snake_min_pheno_2){
    snake_min_pheno_2 = max(file$Snake_min_Pheno) }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_2){
      min_difference_2 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_2){
    max_difference_2 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }
}

  print(paste0("Newt max pheno: ", newt_max_pheno_2))
  print(paste0("Snake max phenot: ", snake_max_pheno_2))
  print(paste0("Newt min pheno: ", newt_min_pheno_2))
  print(paste0("Snake min Pheno: ", snake_min_pheno_2))

  if (newt_max_pheno_2 > snake_max_pheno_2){
    true_max_2 = newt_max_pheno_2 }
  if ( snake_max_pheno_2 > newt_max_pheno_2){
    true_max_2 = snake_max_pheno_2 }

  if (newt_min_pheno_2 < snake_min_pheno_2){
    true_min_2 = newt_min_pheno_2 }
  if ( snake_min_pheno_2 < newt_min_pheno_2){
    true_min_2 = snake_min_pheno_2 }
```

@@

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  #ylim(0, true_max_2)+
  scale_y_log10(limits=c(true_min_2+0.5, true_max_2))+
  geom_line(aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash")+
  ggtitle("1sim: Phenotype Measurements for Newts and Snakes") +
  xlab("Generation") + ylab("Average Phenotypes (Log)")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
 p <- p +
  geom_line(data=file, aes(y = Newt_mean_Pheno), color = "darkred") + 
  geom_line(data=file, aes(y = Snake_mean_Pheno), color="steelblue", linetype="twodash") 
  #Sys.sleep(2)

@@

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=gen)) +
  xlim(0, 1000)+
  ylim(min_difference_2, max_difference_2)+
  #scale_y_continuous(trans=log10_trans(), limits=c(min_difference, max_difference))+
  #scale_y_log10()+
  #scale_y_log10(limits=c(min_difference_2, max_difference_2))+
  geom_line(aes(y = abs(Snake_mean_Pheno - Newt_mean_Pheno)), color = "mediumseagreen") + 
    ggtitle("1sim: Difference Between Phenotypes (Snakes-Newts)") +
  xlab("Generation") + ylab("Average Difference")+
  theme_bw()

@@

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=1:144)) +
  xlim(0, 145)+
  #ylim(newt_min_pheno_1, newt_max_pheno_1)+
  geom_point(aes(x = 1, y = Newt_mean_Pheno[1]), color = darken("darkred")) +
  geom_point(aes(x = 1, y = Newt_mean_Pheno[50]), color = lighten("darkred")) +
  geom_point(aes(x = 1, y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
  geom_point(aes(x = 1, y = Snake_mean_Pheno[50]), color = lighten("steelblue")) +
  ggtitle("1sim: Phenotype Change") +
  xlab("Simulation number") + ylab("Phenotype")+
  theme_bw()
i=1
for (current_file in files){

  file <- read.table(current_file, header = TRUE)
 p <- p + geom_point(data= file, x = i, aes(y = Newt_mean_Pheno[1]), color = darken("darkred")) +
   geom_point(data= file,x = i, aes(y = Newt_mean_Pheno[50]), color = lighten("darkred"))  + geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[1]), color = darken("steelblue")) +
  geom_point(data= file, x = i, aes(y = Snake_mean_Pheno[50]), color = lighten("steelblue"))
 i = i+1
}

@@

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=Newt_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred") + 
  ggtitle("1sim: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()
q <- ggplot(file1, aes(x=Snake_mean_Pheno)) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(Snake_mean_Pheno)*10)), color = "steelblue") + 
  ggtitle("1sim: Newt trasnformed vs un-trasformed") +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()

  file <- read.table(current_file, header = TRUE)
 p <- p + geom_line(data=file, aes(y = (log(Newt_mean_Pheno)*10)), color = "darkred")

 q <- q + geom_line(data=file, aes(y = (log(Snake_mean_Pheno)*10)), color="steelblue", linetype="twodash")
}

@@

```{r gathering data for dif var for msprim sim and slim, echo=FALSE}
newt_max_pheno_3 = 0
snake_max_pheno_3 = 0
newt_min_pheno_3 = 0
snake_min_pheno_3 = 0
true_max_3 = 0
true_min_3 = 0
max_difference_3 = 0
min_difference_3 = 0

@@

  file <- read.table(current_file, header = TRUE)
  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  #print(max(file$Newt_max_Pheno, na.rm = TRUE))
  #print(max(file$Snake_max_Pheno, na.rm = TRUE))

  if (as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) > newt_max_pheno_3){
    newt_max_pheno_3 = as.numeric(max(file$Newt_max_Pheno, na.rm = TRUE)) }

  if (as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) > snake_max_pheno_3){
    snake_max_pheno = as.numeric(max(file$Snake_max_Pheno, na.rm = TRUE)) }

  if (as.numeric(min(file$Newt_min_Pheno, na.rm = TRUE)) < newt_min_pheno_3){
    newt_min_pheno_3 = as.numeric(max(file$Newt_min_Pheno, na.rm = TRUE)) }

  if (as.numeric(max(file$Snake_min_Pheno, na.rm = TRUE)) < snake_min_pheno_3){
    snake_min_pheno_3 = as.numeric(max(file$Snake_min_Pheno, na.rm = TRUE)) }

 if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) < min_difference_3){
    min_difference_3 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  if (as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE)) > max_difference_3){
    max_difference_3 = as.numeric(max(file$Snake_mean_Pheno, na.rm = TRUE)) - as.numeric(min(file$Newt_mean_Pheno, na.rm = TRUE))
  }

  print(paste0("Newt max pheno: ", newt_max_pheno_3))
  print(paste0("Snake max phenot: ", snake_max_pheno_3))
  print(paste0("Min pheno dif: ", min_difference_3))
  print(paste0("Max Pheno dif: ", max_difference_3))

  if (newt_max_pheno_3 > snake_max_pheno_3){
    true_max_3 = newt_max_pheno_3 }
  if ( snake_max_pheno_3 > newt_max_pheno_3){
    true_max_3 = snake_max_pheno_3 }

  if (newt_min_pheno_3 < snake_min_pheno_3){
    true_min_3 = newt_min_pheno_3 }
  if ( snake_max_pheno_3 < newt_max_pheno_3){
    true_min_3 = snake_min_pheno_3 }
```
some of these values are in quotes, why?

>>>>

  file$Newt_max_Pheno[file$Newt_max_Pheno == "NULL"] <- NA
  file$Snake_max_Pheno[file$Snake_max_Pheno == "NULL"] <- NA
  file$Newt_min_Pheno[file$Newt_min_Pheno == "NULL"] <- NA
  file$Snake_min_Pheno[file$Snake_min_Pheno == "NULL"] <- NA
  file$Newt_mean_Pheno[file$Newt_mean_Pheno == "NULL"] <- NA
  file$Snake_mean_Pheno[file$Snake_mean_Pheno == "NULL"] <- NA
  file$Newt_mean_Pheno <- lapply(file$Newt_mean_Pheno,as.numeric)
  file$Snake_mean_Pheno <- lapply(file$Snake_mean_Pheno,as.numeric)
  file$Newt_max_Pheno <- lapply(file$Newt_max_Pheno,as.numeric)
  file$Snake_max_Pheno <- lapply(file$Snake_max_Pheno,as.numeric)
  file$Newt_min_Pheno <- lapply(file$Newt_min_Pheno,as.numeric)
  file$Snake_min_Pheno <- lapply(file$Snake_min_Pheno,as.numeric)

  mean = mean(c(as.numeric(file$Newt_mean_Pheno), as.numeric(file$Snake_mean_Pheno)), na.rm = TRUE)
  sd = sd(c(as.numeric(file$Newt_mean_Pheno), as.numeric(file$Snake_mean_Pheno)), na.rm = TRUE)
  mean_mean_dif = mean(as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno),na.rm = TRUE)
  sd_mean_dif = sd(as.numeric(file$Snake_mean_Pheno) - as.numeric(file$Newt_mean_Pheno),na.rm = TRUE)

    if (max(as.numeric(file$Newt_max_Pheno), na.rm = TRUE) > newt_max_pheno_1){
    newt_max_pheno_1 = max(as.numeric(file$Newt_max_Pheno), na.rm = TRUE) }

  if (max(as.numeric(file$Snake_max_Pheno), na.rm = TRUE) > snake_max_pheno_1){
    snake_max_pheno_1 = max(as.numeric(file$Snake_max_Pheno), na.rm = TRUE) }

  if (min(as.numeric(file$Newt_min_Pheno), na.rm = TRUE) < newt_min_pheno_1){
    newt_min_pheno_1 = min(as.numeric(file$Newt_min_Pheno), na.rm = TRUE) }

  if (min(as.numeric(file$Snake_min_Pheno), na.rm = TRUE) < snake_min_pheno_1){
    snake_min_pheno_1 = min(as.numeric(file$Snake_min_Pheno), na.rm = TRUE) }

  if (min(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - max(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE) < min_difference_1){
    min_difference_1 = min(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - max(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE)
  }

  if (max(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - min(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE) > max_difference_1){
    max_difference_1 = max(as.numeric(file$Snake_mean_Pheno), na.rm = TRUE) - min(as.numeric(file$Newt_mean_Pheno), na.rm = TRUE)
  }
  }

@@

untrasform <- function(files, the_mean, the_sd, title1, title2, is_log=FALSE){

file1 <- read.table(files[1], header = TRUE)
p <- ggplot(file1, aes(x=as.numeric(Newt_mean_Pheno))) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(as.numeric(Newt_mean_Pheno))*10)), color = "darkred") + 
  ggtitle(title1) +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()
q <- ggplot(file1, aes(x=as.numeric(Snake_mean_Pheno))) +
  #ylim(0, true_max_1)+
  geom_line(aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color = "steelblue") + 
  ggtitle(title2) +
  xlab("Trasnformed") + ylab("Untransformed")+
  theme_bw()

 q <- q + geom_line(data=file, aes(y = (log(as.numeric(Snake_mean_Pheno))*10)), color="steelblue", linetype="twodash", na.rm = FALSE)
}
return(list(p,q))

@@

files <- list.files(path="~/Desktop/pheno_test_1000_old/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

title1 = "Wrong1sim: Newt trasnformed vs un-trasformed"
title2 = "Wrong1sim: Snake trasnformed vs un-trasformed"
graph = untrasform(files, my_mean, my_sd, title1, title2, is_log=FALSE)
graph[1]
graph[2]

@@

```{r data 1 msprime photype graph, echo=FALSE}
files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)

@@

files <- list.files(path="~/Desktop/pheno_test_1000/text_files/test", pattern="*.txt", full.names=TRUE, recursive=FALSE)
title = "1sim: Phenotype Measurements for Newts and Snake"
q = phenotype_graph(files, my_mean, my_sd, title, is_log = TRUE)
p = phenotype_graph(files, my_mean, my_sd, title)
q
p 
```

@@

title = "1sim: Difference Between Phenotypes (Snakes-Newts)"
p = differnce_graph(files, mean_mean_dif, sd_mean_dif, title, is_log=FALSE)

@@

title = "1sim: Phenotype Change"
p=phenotype_change_graph(files, my_mean, my_sd, title, is_log=FALSE)

@@

title1 = "1som: Newt trasnformed vs un-trasformed"
title2 = "g1sim: Snake trasnformed vs un-trasformed"
graph = untrasform(files, my_mean, my_sd, title1, title2, is_log=FALSE)
graph[1]
graph[2]

@@

```{r gathering data for dif var for msprim sim and slim, echo=FALSE}

@@

```
some of these values are in quotes, why?
